\textsf{Are frontier models superhuman chemists?}

### 2024-03-11 src/tex/ms.tex

>>>>

To maintain the consistency with the training, we employ distinct prompt templates in general tailored for completion models and instruction-tuned models. 
We pose instruction or impose constraints on the models within these templates to receive response in a specific format so that a robust, fair and consistent parsing can be performed as explained in \Graf{sec:parsing}.
Certain models are trained with special annotations and LaTeX syntax for scientific notations, chemical reactions, or symbols embedded within the text. 
For example, all the SMILES representations are encapsulated within \texttt{[START_SMILES][\text backslash END_SMILES]} in Galactica\cite{taylor2022galactica}.
Our prompting strategy consistently adheres to  these details in a model-specific manner by post-processing \latex syntax, chemical symbols, chemical equations and physical units (by either adding or removing wrappers).
